Tempo Analysis: The Sound of Teaching Music 1

### 2022-07-03 experiment-1/analysis/stats/ioi.Rmd
correct typos
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# plot
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
# statistics
if (!require("afex")) {install.packages("afex"); require("afex")}
if (!require("rstatix")) {install.packages("rstatix"); require("rstatix")}
```

@@

### Statistics
#### Normality check
- Violate the normality for differences between the two conditions

@@

```{r ioi-art-trial, echo = FALSE}
ioi_art_trial
```

>>>>

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# plot
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
# statistics
if (!require("afex")) {install.packages("afex"); require("afex")}
if (!require("rstatix")) {install.packages("rstatix"); require("rstatix")}

# chunk option
knitr::opts_chunk$set(warning = FALSE)
```

@@

### Statistics
#### Normality check
- The Shapiro-Wilk test showed that the normality for differences between the two conditions was violated.

@@

```{r ioi-art-trial, echo = FALSE}
# For each individual
ioi_art_trial
```
